### 2020-02-19 ISLR/08_Tree-Based-Methods.rmd
tree work
tree work

par(mfrow = c(1,1))
plot(rf)
text(rf, pretty = 0)
```

@@

@@

>>>>

par(mfrow = c(1,1))
plot(carseat.tree)
text(carseat.tree, pretty = 0)
```

@@

```{r}
p <- ncol(carseats)

ntrees <- seq(0, 500, 25)
rf.error <- numeric(length(ntrees))

for(i in 1:length(ntrees))
{
   carseats.rf <- randomForest(Sales ~ ., data = carseats.train, mtry = p, n.trees = ntrees[i])

   pred <- predict(carseats.rf, newdata = carseats.test)

   rf.error[i] <- mean((pred - carseats.test$Sales)^2)
}

lowest.error <- which.min(rf.error)

results <- data.table(trees = ntrees, error = rf.error)[, lowest := .I == lowest.error]

ggplot(results, aes(trees, error, fill = lowest)) +
   geom_bar(stat = "identity") +
   labs(title = paste0("lowest error: #", ntrees[lowest.error]))

@@

e.) Use random forest to analyize this data. What test MSE do you obtain? Use the importance() fucntion to determine which variables are most important. Describe the effect of m, the number of variables considered at each split, on the error obtained.

```{r}
p <- ncol(carseats)

mtry <- seq(1, p)

rf.error <- numeric(p)

for(i in 1:p)
{
   carseats.rf <- randomForest(Sales ~ ., data = carseats.train, mtry = mtry[i], n.trees = 250)

   pred <- predict(carseats.rf, newdata = carseats.test)

   rf.error[i] <- mean((pred - carseats.test$Sales)^2)
}

lowest.error <- which.min(rf.error)

results <- data.table(mtry = mtry, error = rf.error, lowest = mtry == lowest.error)

ggplot(results, aes(mtry, error, fill = lowest)) +
   geom_bar(stat = "identity")
```
